Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-07-12 vesicle_code/docs/adhesion/adhesion.tex
put in intrinsic viscosity numbers

Finally, we investigate the rheology of a suspension of a doublet by
computing the effective viscosity of a doublet and compare it to the
effective viscosity of a single tank-treading vesicle. The effective
viscosity is defined as the viscosity of a homogeneous Newtonian fluid
with the same energy dissipation per macroscopic element of fluid.  In a
simple shear flow, the intrinsic viscosity, $[\mu]$ is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\chi \mu_0 (T_e - T_i)} \int_{T_i}^{T_e} 
  \langle \tau_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \tau \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds,
\end{align*}
$\phi$ is the area fraction of vesicles, $\tau$ is the stress due to the
vesicles, $\langle \cdot \rangle$ is the spatial average, $|\omega|$ is
the total area of both vesicles, and $\xxi$ is the traction as defined
in equation~\eqref{eqn:traction}.  In
Figure~\ref{fig:shearIntrinsicViscosity}(a), we compare the intrinsic
viscosity of a single tank-treading vesicle to a doublet.  To validate
our simulations, we superimpose (black marks) the intrinsic viscosity
calculated by Ghigliotti {\em et
al.}~\cite{GhigliottiBibenMisbah2010_JFM}.  The presence of the doublet
slightly increases the intrinsic viscosity at all the reduced areas.  To
further characterize the effect of adhesion, in
Figure~\ref{fig:shearIntrinsicViscosity}(b) we decompose the intrinsic
viscosity into the contributions from the bending and tension (blue),
and the contribution from the adhesion (red).  We also superimpose the
intrinsic viscosity of a single tank-treading vesicle (dashed curve) to
demonstrate that the bending and tension of the doublet behave
similarly, but not identically, to a dilute suspensions of non-adhering
tank-treading vesicles.  We see that the effect of the adhesion on the
intrinsic viscosity is largest for vesicles with small reduced areas.

>>>>

Finally, we investigate the rheology of a suspension of a doublet by
computing the effective viscosity of a doublet and compare it to the
effective viscosity of a single tank-treading vesicle. The effective
viscosity is defined as the viscosity of a homogeneous Newtonian fluid
with the same energy dissipation per macroscopic element of fluid.  In a
simple shear flow, the intrinsic viscosity, $[\mu]$ is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\chi \mu_0 (T_e - T_i)} \int_{T_i}^{T_e} 
  \langle \tau_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \tau \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds,
\end{align*}
$\phi$ is the area fraction of vesicles, $\tau$ is the stress due to the
vesicles, $\langle \cdot \rangle$ is the spatial average, $|\omega|$ is
the total area of both vesicles, and $\xxi$ is the traction as defined
in equation~\eqref{eqn:traction}.  In
Figure~\ref{fig:shearIntrinsicViscosity}(a), we compare the intrinsic
viscosity of a single tank-treading vesicle to a doublet with Hamaker
constant $\mathcal{H} = 0.7$, separation distance $\delta = 0.4$, and
shear rate $\chi = 0.5$.  To validate our simulations, we superimpose
(black marks) the intrinsic viscosity calculated by Ghigliotti {\em et
al.}~\cite{GhigliottiBibenMisbah2010_JFM}.  The presence of the doublet
slightly increases the intrinsic viscosity at all the reduced areas.
We also compute the intrinsic viscosity of a doublet with $\Delta A =
0.9$, $\chi = 0.5$, and $\mathcal{H} = 2.1$.  Again, this doublet has a
similar period to the case $\mathcal{H} = 2.1$.  At this larger Hamaker
constant, the effective viscosity increases slightly from $1.97$ to
$2.06$.

To further characterize the effect of adhesion, in
Figure~\ref{fig:shearIntrinsicViscosity}(b) we decompose the intrinsic
viscosity into the contributions from the bending and tension (blue),
and the contribution from the adhesion (red).  We also superimpose the
intrinsic viscosity of a single tank-treading vesicle (dashed curve) to
demonstrate that the bending and tension of the doublet behave
similarly, but not identically, to a dilute suspensions of non-adhering
tank-treading vesicles.  We see that the effect of the adhesion on the
intrinsic viscosity is largest for vesicles with small reduced areas.
We also decompose the intrinsic viscosity contributions of the doublet
with $\mathcal{H} = 2.1$ and $\Delta A = 0.9$.  When compared with the
smaller Hamaker constant, the intrinsic viscosity contribution due to
bending and tension is reduced from $1.85$ to $1.71$, and the
contribution due to adhesion is increased from $0.12$ to $0.36$.
Therefore, as the Hamaker constant increases, the increase in the
intrinsic viscosity is due to the adhesive force rather than the bending
and tension.
